Exploratory Plots

### 2020-10-08 exploratory/2020/sub3_fit_all-seqs.Rmd
Set random seed

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      fig.path = "figures/"
                      )
```
```{r lib}
library(cowplot)
library(ggtext)
library(here)
library(knitr)
library(tidyverse)
theme_set(theme_classic())
color_palette <- RColorBrewer::brewer.pal(4, "Dark2")
dataset_colors <- c(
  human = color_palette[[3]],
  marine = color_palette[[1]],
  mouse = color_palette[[4]],
  soil = color_palette[[2]]
)
full_join_files <- function(filenames) {
  filenames %>% 
  lapply(read_tsv) %>% 
  reduce(full_join)
}
```
```{r download_data}
dat <- c('subworkflows/3_fit_sample_subset/results/all-seqs/sensspec.tsv',
         'subworkflows/3_fit_sample_subset/results/all-seqs/benchmarks.tsv',
         'subworkflows/3_fit_sample_subset/results/all-seqs/input_sizes.tsv',
         'subworkflows/3_fit_sample_subset/results/all-seqs/sensspec.tsv',
         'subworkflows/3_fit_sample_subset/results/all-seqs/fraction_reads_mapped.tsv') %>% 
  here() %>% 
  full_join_files() %>% 
  mutate(num_total_seqs = num_ref_seqs + num_sample_seqs,
         gaps_frac = n_gaps / total_chars,
         mem_mb = max_rss,
         mem_gb = mem_mb / 1024)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      fig.path = "figures/"
                      )
```
```{r lib}
library(cowplot)
library(ggtext)
library(here)
library(knitr)
library(tidyverse)
theme_set(theme_classic())
color_palette <- RColorBrewer::brewer.pal(4, "Dark2")
dataset_colors <- c(
  human = color_palette[[3]],
  marine = color_palette[[1]],
  mouse = color_palette[[4]],
  soil = color_palette[[2]]
)
full_join_files <- function(filenames) {
  filenames %>% 
  lapply(read_tsv) %>% 
  reduce(full_join)
}
set.seed(2018)
```
```{r download_data}
dat <- c('subworkflows/3_fit_sample_subset/results/all-seqs/sensspec.tsv',
         'subworkflows/3_fit_sample_subset/results/all-seqs/benchmarks.tsv',
         'subworkflows/3_fit_sample_subset/results/all-seqs/input_sizes.tsv',
         'subworkflows/3_fit_sample_subset/results/all-seqs/sensspec.tsv',
         'subworkflows/3_fit_sample_subset/results/all-seqs/fraction_reads_mapped.tsv') %>% 
  here() %>% 
  full_join_files() %>% 
  mutate(num_total_seqs = num_ref_seqs + num_sample_seqs,
         gaps_frac = n_gaps / total_chars,
         mem_mb = max_rss,
         mem_gb = mem_mb / 1024)
